oREV item selection and analysis

### 2022-11-23 analysis/orev_item_selection.Rmd
add plots for 1PL sel

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidybayes)
library(brms)
library(rstan)
library(loo)
library(coda)

@@

```{r}
items <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(targetWord)
easiness_rasch <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(threshold_mode)
infit <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>% pull(infit_mode)
outfit <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(outfit_mode)
disc_2PL <- coef2PL$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
pkd <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(pareto_k)
```

@@

  for(j in 2:2){

  for (i in 38:40) {

@@

saveRDS(irt_comp_size, "../saves/irt_comp_size.rds")

irt_comp_size <- readRDS("../saves/irt_comp_size.rds")

@@

saveRDS(rasch_selected_items, "../saves/selected_items_rasch.rds")
```

@@

```{r}
icc1_guess_sel %>% 
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  geom_line() +
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  scale_color_viridis_c(name = "AoA") +
  labs(title = "ICCs for the 1PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```

@@

```{r}
irt1_guess_dif_sex_sel <-  brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (0+ sex | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  prior = prior_1pl_guess,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

@@

```{r}
irt1_guess_dif_order_sel <- brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (0+ order | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  prior = prior_1pl_guess,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

@@

```{r}
loo_compare(irt1_guess_sel, irt1_guess_dif_order_sel, irt1_guess_dif_sex_sel)%>%as_tibble(rownames = "model")

brms::bayes_R2(irt1_guess)
```

@@

```{r}
rel_dat <- irt_dat%>%
  select(-sex, -order)%>%
  filter(targetWord %in% rasch_selected_items)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidybayes)
library(brms)
library(rstan)
library(loo)
library(coda)
library(testing)
library(geomtextpath)

@@

```{r}
items <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(targetWord)
easiness_rasch <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(threshold_mode)
infit <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>% pull(infit_mode)
outfit <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(outfit_mode)
disc_2PL <- coef2PL$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
pkd <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(pareto_k)

x <- sample(pkd, 20)
mean(x)

@@

  for(j in 1:5){

  for (i in 10:15) {

@@

#saveRDS(irt_comp_size, "../saves/irt_comp_size.rds")

#irt_comp_size <- readRDS("../saves/irt_comp_size.rds")

@@

saveRDS(rasch_selected_items, "../saves/selected_items_rasch.rds")

rasch_selected_items <- readRDS("../saves/selected_items_rasch.rds")
```

@@

```{r}
icc1_guess_sel %>% 
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  #geom_line() +
  geom_textline(aes(label = item)) +
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  scale_color_viridis_c(name = "AoA") +
  labs(title = "ICCs for the 1PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```

```{r}
ggsave("../graphs/ICC_1PL_sel.png", height = 6, width = 10, scale = 1)
```

@@

```{r}
irt1_guess_dif_sex_sel <-  brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (0+ sex | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  prior = prior_1pl_guess,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000,
  threads = threading(8), #to speed things up, comment out if not on a cluster
  backend = "cmdstanr" #to speed things up, comment out if not on a cluster
)%>%add_criterion(c("loo","waic"))

@@

```{r}
irt1_guess_dif_order_sel <- brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (0+ order | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  prior = prior_1pl_guess,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000,
  threads = threading(8), #to speed things up, comment out if not on a cluster
  backend = "cmdstanr" #to speed things up, comment out if not on a cluster
)%>%add_criterion(c("loo","waic"))

@@

```{r}
loo_compare(irt1_guess_sel, irt1_guess_dif_order_sel, irt1_guess_dif_sex_sel)%>%as_tibble(rownames = "model")
```

@@

```{r}
rel_dat <- irt_dat%>%
  select(-sex, -order, -aoa_german_comb)%>%
  filter(targetWord %in% rasch_selected_items)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)
